Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-25 mr-review.Rmd
added text about JASA papers

@kang_instrumental_2016

@@

@windmeijer_use_2019

@@

In efforts to develop MR methods that are robust to correlated horizontal pleiotropy, 
@brown_welch-weighted_2021 present Welch-weighted Egger regression. Their flexible model 
accommodates both uni-directional and bi-directional effects between exposure and outcome. 
@brown_welch-weighted_2021 specifies their model via Equations \@ref(eq:wwer). They denote 
the two traits by $A$ and $B$, the SNP genotypes matrix by $X$, and the unobserved confounder by $U$. $Z_U$, $Z_A$ and $Z_B$ denote the indicator vectors of zeros and ones to indicate which . Note that the model is agnostic with regards to which is the 
outcome and which the exposure, so we follow the authors' notation here.

>>>>

@kang_instrumental_2016 developed a LASSO-based method, sisVIVE, to 
identify invalid SNP instruments [@tibshirani1996regression]. sisVIVE's 
advantage over earlier methods is that it doesn't require the analyst 
to know which SNP instruments are valid. Instead, it requires that at 
least 50\% of the instruments be valid. sisVIVE outperforms two-stage 
least squares in many ways and performs similar to oracle two-stage 
least squares. Simulations and data analysis results reveal that 
sisVIVE is robust to possibly invalid instruments.

@windmeijer_use_2019, building on the research from 
@kang_instrumental_2016, implemented an adaptive LASSO-based estimator 
after recognizing that sisVIVE misclassifies valid SNP instruments as 
invalid when the invalid SNP instruments have strong effects on the 
exposure. Consistent selection of invalid SNP instruments, they found, 
depends on SNP instrument correlations. To address this issue, @windmeijer_use_2019 
proposed a median estimator with consistency that doesn't 
depend on SNP instrument-exposure association strength or the SNP instrument 
correlation structure. They then applied methods from @zou2006adaptive to 
achieve a consistent estimator with the same distribution as the oracle 
two-stages least squares.

@@

@windmeijer_use_2019
@kang_instrumental_2016

@@

To develop MR methods that are robust to correlated horizontal pleiotropy, 
@brown_welch-weighted_2021 present Welch-weighted Egger regression. Their flexible model 
accommodates both uni-directional and bi-directional effects between exposure and outcome. 
@brown_welch-weighted_2021 specifies their model via Equations \@ref(eq:wwer). They denote 
the two traits by $A$ and $B$, the SNP genotypes matrix by $X$, and the unobserved confounder by $U$. $Z_U$, $Z_A$ and $Z_B$ denote the indicator vectors of zeros and ones to indicate which . Note that the model is agnostic with regards to which is the 
outcome and which the exposure, so we follow the authors' notation here.
